% REV02 Fri 23 Jul 2021 17:19:30 WIB
% REV01 Sun 27 Jun 2021 07:29:17 WIB
% START Tue 04 May 2021 13:55:16 WIB

\chapter{SETTING TRAPS}

Plashwater Weir Mill Lock looked tranquil and pretty on an evening in
the summer time. A soft air stirred the leaves of the fresh green trees,
and passed like a smooth shadow over the river, and like a smoother
shadow over the yielding grass. The voice of the falling water, like
the voices of the sea and the wind, were as an outer memory to a
contemplative listener; but not particularly so to Mr Riderhood, who sat
on one of the blunt wooden levers of his lock-gates, dozing. Wine must
be got into a butt by some agency before it can be drawn out; and the
wine of sentiment never having been got into Mr Riderhood by any agency,
nothing in nature tapped him.

As the Rogue sat, ever and again nodding himself off his balance, his
recovery was always attended by an angry stare and growl, as if, in the
absence of any one else, he had aggressive inclinations towards himself.
In one of these starts the cry of ‘Lock, ho! Lock!’ prevented his
relapse into a doze. Shaking himself as he got up like the surly brute
he was, he gave his growl a responsive twist at the end, and turned his
face down-stream to see who hailed.

It was an amateur-sculler, well up to his work though taking it easily,
in so light a boat that the Rogue remarked: ‘A little less on you, and
you’d a’most ha’ been a Wagerbut’; then went to work at his windlass
handles and sluices, to let the sculler in. As the latter stood in his
boat, holding on by the boat-hook to the woodwork at the lock side,
waiting for the gates to open, Rogue Riderhood recognized his ‘T’other
governor,’ Mr Eugene Wrayburn; who was, however, too indifferent or too
much engaged to recognize him.

The creaking lock-gates opened slowly, and the light boat passed in as
soon as there was room enough, and the creaking lock-gates closed upon
it, and it floated low down in the dock between the two sets of gates,
until the water should rise and the second gates should open and let it
out. When Riderhood had run to his second windlass and turned it, and
while he leaned against the lever of that gate to help it to swing
open presently, he noticed, lying to rest under the green hedge by the
towing-path astern of the Lock, a Bargeman.

The water rose and rose as the sluice poured in, dispersing the scum
which had formed behind the lumbering gates, and sending the boat up,
so that the sculler gradually rose like an apparition against the light
from the bargeman’s point of view. Riderhood observed that the bargeman
rose too, leaning on his arm, and seemed to have his eyes fastened on
the rising figure.

But, there was the toll to be taken, as the gates were now complaining
and opening. The T’other governor tossed it ashore, twisted in a piece
of paper, and as he did so, knew his man.

‘Ay, ay? It’s you, is it, honest friend?’ said Eugene, seating himself
preparatory to resuming his sculls. ‘You got the place, then?’

‘I got the place, and no thanks to you for it, nor yet none to Lawyer
Lightwood,’ gruffly answered Riderhood.

‘We saved our recommendation, honest fellow,’ said Eugene, ‘for the next
candidate--the one who will offer himself when you are transported or
hanged. Don’t be long about it; will you be so good?’

